Cover Times of Random Walks

### 2019-04-29 paper.tex
minor

\abstract{
The cover time of a graph is the time it takes for a random walk to
visit all of its vertices.
We provide a detailed overview for a variety of cover time topics:
We begin by investigating the cover time of small and structured graphs but
quickly need a more robust strategy for larger, unstructured ones.
We apply more general probablistic arguments and an important electrical
network relationship to identify bounds.
Finally, we describe the limiting distribution of the cover time of
complete graphs with self-edges and apply our analysis to an intuitive example.
}

>>>>

\abstract{
The cover time of a graph is the number of steps of a
discrete random walk until every vertex has been visited at leastonce.
This senior work provides a detailed overview
of a variety of cover time topics.
We begin by investigating the cover time of small and structured graphs but
quickly find that we need
require a less precise strategy for larger, unstructured ones.
We apply more general probablistic arguments and an important electrical
network relationship to identify bounds for arbitrary graphs.
Finally, we describe the limiting distribution of the cover time of
complete graphs with self-edges.
}
